embedplyr: Tools for Working With Text Embeddings

### 2025-08-05 README.Rmd
performance vignette
addresses issue #2

Whereas indexing a regular matrix by rownames gets slower as the number of rows increases, embedplyr's hash table indexing means that token embeddings can be retrieved in milliseconds even from models with millions of rows.

>>>>

Whereas indexing a regular matrix by rownames gets slower as the number of rows increases, embedplyr's hash table indexing means that token embeddings can be retrieved in milliseconds even from models with millions of rows (see the [performance vignette](vignettes/performance.html)).

### 2025-08-05 paper/paper.Rmd
performance vignette
addresses issue #2

Whereas indexing a regular matrix by rownames gets slower as the number of rows increases, **embedplyr**'s hash table indexing means that token embeddings can be retrieved in milliseconds even from models with millions of rows.

>>>>

Whereas indexing a regular matrix by rownames gets slower as the number of rows increases, **embedplyr**'s hash table indexing means that token embeddings can be retrieved in milliseconds even from models with millions of rows (see the [performance vignette](vignettes/performance.html)).
